TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-17 article.tex
Paper TTT

%% - \Abstract{} almost as usual
\Abstract{
  Abstract
}

\Keywords{, \proglang{Python}}
\Plainkeywords{Python}

@@

@@

%% - In principle "as usual".
%% - But should typically have some discussion of both _software_ and _methods_.
%% - Use \proglang{}, \pkg{}, and \code{} markup throughout the manuscript.
%% - If such markup is in (sub)section titles, a plain text version has to be
%%   added as well.
%% - All software mentioned should be properly \cite-d.
%% - All abbreviations should be introduced.
%% - Unless the expansions of abbreviations are proper names (like "Journal
%%   of Statistical Software" above) they should be in sentence case (like
%%   "generalized linear models" below).

@@

\begin{leftbar}
The introduction is in principle ``as usual''. However, it should usually embed both the implemented \emph{methods} and the \emph{software} into the respective relevant literature.
For the latter both competing and complementary software should be discussed (within the same software environment and beyond), bringing
out relative (dis)advantages. All software mentioned should be properly
\verb|\cite{}|d. (See also Appendix~\ref{app:bibtex} for more details on
\textsc{Bib}{\TeX}.)

For writing about software JSS requires authors to use the markup
\verb|\proglang{}| (programming languages and large programmable systems),
\verb|\pkg{}| (software packages), \verb|\code{}| (functions, commands,
arguments, etc.).
If there is such markup in (sub)section titles (as above), a plain text version has to be provided in the {\LaTeX} command as well.
Below we also illustrate how abbrevations should be introduced and citation commands can be employed.
See the {\LaTeX} code for more details.
\end{leftbar}

@@

\subsection{Propiedades}\label{sec:propiedades}

@@

\subsubsection*{Multiplicacion de normales}  
\begin{equation}\label{eq:multiplicacion_normales}
\begin{split}
 \int_{-\infty}^{\infty} N(x|\mu_x,\sigma_x^2)N(x|\mu_y,\sigma_y^2) \, dx  &  \overset{*}{=} \int_{-\infty}^{\infty}  \underbrace{N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2)}_{\text{constante}} N(x|\mu_{*},\sigma_{*}^2) dx \\
 & = N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2) \underbrace{\int_{-\infty}^{\infty}  N(x|\mu_{*},\sigma_{*}^2) dx}_{1} \\
 & = N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2) 
\end{split}
\end{equation}

@@

\subsubsection*{Integrales con funci\'on indicadora}
\begin{equation}\label{eq:integral_con_indicadora} 
\begin{split}
 \int_{-\infty}^{\infty}  \int_{-\infty}^{\infty}  \mathbb{I}(x=h(y,z)) f(x) g(y)\, dx\, dy &=  \int_{-\infty}^{\infty} \int_{h(y,z)}^{h(y,z)} f(h(y,z)) g(y)\, dx\, dy\\
 & = \int_{-\infty}^{\infty} f(h(y,z)) g(y) dy 
 %& \propto \int f(h(y,z)) g(y) dy 
\end{split}
\end{equation}

\subsubsection*{Simetr\'ia de normales}
\begin{equation}\label{eq:simetria}
 N(x|\mu,\sigma^2) = N(\mu|x,\sigma^2) = N(-\mu|-x,\sigma^2) = N(-x|-\mu,\sigma^2) 
\end{equation}

\subsubsection*{Derivada de la acumulada normal}
\begin{equation}\label{eq:phi_norm}
 \frac{\partial}{\partial x} \Phi(x|\mu,\sigma^2) = N(x|\mu,\sigma^2)
\end{equation}

\subsubsection*{Distribuci\'on normal estandarizada}
\begin{equation}\label{eq:estandarizar}
 X \sim N(\mu,\sigma^2) \Rightarrow \frac{X-\mu}{\sigma} \sim N(0,1)
\end{equation}

\subsection{Ejemplo 2 vs 2}

@@

\subsubsection{Mensajes descendentes}

@@

\section{Prior predictive y evidencia}

La evidencia es otro nombre para el Prior predictive.

\begin{equation*}
\underbrace{P(\text{Belief}|\text{Data})}_{\text{\scriptsize Posterior}} = \frac{\overbrace{P(\text{Data}|\text{Belief})}^{\text{\scriptsize Likelihood}} \overbrace{P(\text{Belief})}^{\text{\scriptsize Prior}} }{\underbrace{P(\text{Data})}_{\hfrac{\hfrac{\text{\scriptsize Evidence or}}{\text{\scriptsize Average likelihood}}}{\text{\scriptsize Prior Predictive}} } }
\end{equation*}

@@

\section{Aproximacion de la posterior (DRAFT)}

La probabilidad de una diferencia cuando se conoce el resultado (Eq.~\ref{eq:p_d}) es una Normal truncada.

\begin{equation}\label{eq:p_d}
\begin{split}
 P(d_1) & \overset{\hfrac{\text{eq}}{\ref{eq:marginal}}}{=}   \prod_{h \in n(d_1)} m_{h \rightarrow d_1} \overset{\hfrac{\text{fig}}{\ref{modelo_trueskill_2vs2}}}{=} m_{f_{d_1} \rightarrow d_1}(d_1) \, m_{f_r \rightarrow d_1}(d_1) \overset{\hfrac{\text{eq}}{\ref{eq:m_fr_d}}}{\underset{\hfrac{\text{eq}}{\ref{eq:m_d_fd}}}{=}}  m_{f_{d_1} \rightarrow d_1}(d_1) \, m_{d_1 \rightarrow f_{d_1}}(d_1)  \\
 & = N(d_1|\delta,\vartheta) \mathbb{I}(d_1 > 0)
\end{split}
\end{equation}

Para tener una posterior normal lo que se hace es un buscar la normal que m\'as se aproxima a esta normal truncada

@@

\newpage
\section{Posterior exacta multiequipos}

Para calcular la posterior exacta de un equipo $a$ en una partida multiequipos, se puede considerar un factor graph en el que el equipo $a$ es el centro, de modo de poder enviar los mensajes de forma directa.

\begin{figure}[t!]
  \centering
  \scalebox{.75}{\input{modelos/trueskill_factorGraph_versionGeneral_multiequiposExacta.tex}}
  \caption{\small Grafo de factorizaci\'on del modelo \texttt{TrueSkill} alternativo, en el que el equipo un focal $a$ se encuentra en el centro.}
  \label{modelo_trueskill_2vs2}
\end{figure}

\paragraph{$\bm{m_{t_a \rightarrow f_{t_a}}(t_a)}:$}

\section{Full TrueSkill}

\paragraph{\emph{looseLikelihood}$\bm(t_{i+1})$:}

\paragraph{\emph{winLikelihood}$\bm(t_{i})$:}

\begin{equation}
 \begin{split}
  \emph{winLikelihood}(t_{i}) = \int \mathbb{I}(d_i>0) \emph{prior}(t_{i+1}) \widehat{\emph{likelihood}}(d_i)
 \end{split}
\end{equation}

\section{TrueSkill through Time (TTT)}

\begin{mdframed}[backgroundcolor=black!15]
 Note that the following conclusions are based on the idea that original TrueSkill \emph{porceeds through the years (temporal batch) in order, but (within a temporal batch) goes through games outcome in random order}.
 This is not true. 
 Original TrueSkill algorithm does not need any temporal batch for inference.
 So neither goes through games outcome in random order within a year or any other temporal batch.
 By contrast, original TrueSkill sorts games before the inference stage by their game date.
 Sometime it is true, specially in in online game, that we can find users who play more than one game at the same time.
 In this cases it is not clear how to sort those games.
 However, this situation never holds more than a few hours.
 The unsorted games are an exception rather than a rule in original TrueSkill.
 \textbf{So why the authors of TTT adopt temporal batching, unnecessary for the orginal TrueSkill?}
 \textbf{There is a hidden reason for adopting temporal batching, only necessary for TTT?}
 There is no problem if we add new features to an algorithm.
 But in this case, the adoption of this new feature is badly justified.
\end{mdframed}

\begin{mdframed}[backgroundcolor=black!15] 
 What happens if we define very small and very large temporal batch. 
 For example consider the follow three games in temporal order: A beats B, then B beats C and finally C beats A.
 If we define \textbf{short temporal batch} such that only cover one game at a time, then there will be no within convergence step for which the results of inference should be independent of the order of games.
 If we define \textbf{long temporal batch} such that cover all games, then there will be no time steps to propagate information backwards.
\end{mdframed}

\subsection{Convergence}

\begin{table}[t!]
\centering
\begin{tabular}{lllp{7.4cm}}
\hline
Type           & Distribution & Method   & Description \\ \hline
GLM            & Poisson      & ML       & Poisson regression: classical GLM,
                                           estimated by maximum likelihood (ML) \\
\end{tabular}
\caption{\label{tab:overview} Overview of various count regression models. The
table is usually placed at the top of the page (\texttt{[t!]}), centered
(\texttt{centering}), has a caption below the table, column headers and captions
are in sentence style, and if possible vertical lines should be avoided.}
\end{table}

%\bibliography{refs}
\bibliography{../../../licar/bibliografia/Gaming/gaming.bib}

\newpage
\section{Propiedades de las funciones de densidad Normales}

>>>>

@@

%% - \Abstract{} almost as usual
\Abstract{
 \pkg{ttt} package is a \proglang{Python} implementation of TrueSkill Through Time (TTT), an enhancement of TrueSkill algorithm, widely used by the video game industry for skill estimation.
 TTT is a probabilistic model for general pairwise-comparison.
 A nice feature is the use of a single graphical model for the entire history of events.
 The posterior distribution is computed based on an efficient variationl algorithm, known as expectation propagation.
 As a result, the inference procedure requires only a few linear-time iterations over the data.
 This algorithm outperforms competing estimations in terms of model evidence, and scales to millions of parameters.
 We offer an easy to use interface, compatible with the current \code{trueskill} package for \proglang{Python}.  
}

\Keywords{TrueSkill, ranking, skill, education, sports, games, Bayesian inference, \proglang{Python}}
\Plainkeywords{TrueSkill, ranking, skill, education, sports, games,  Bayesian inference, Python}

@@

%% - But should typically have some discussion of both _software_ and _methods_.
%% - Use \proglang{}, \pkg{}, and \code{} markup throughout the manuscript.
%% - If such markup is in (sub)section titles, a plain text version has to be
%%   added as well.
%% - All software mentioned should be properly \cite-d.
%% - All abbreviations should be introduced.
%% - Unless the expansions of abbreviations are proper names (like "Journal of Statistical Software" above) they should be in sentence case (like "generalized linear models" below).

@@

TrueSkill Through Time (TTT) is a probabilistic model for general pairwise comparison.

The most commonly definition of skill, used in educational and sports contexts, rely on the agents' chance to solve a problem or to win against a competitor.
It is worth noting this is esentially a pairwise comparition and not an absolute value of individuals.

Models for pairwise comparisons have been studied for almost a century.
Thurstone \cite{thurstone1927-psychophysicalAnalysis,thurstone1927-comparativeJugement} propose the first and basic generative model, and show how to infer a hidden perception relative to a reference stimulus and a discriminal process.

\cite{glickman2013-zermelo1928}

This model is equivalent to Elo. The skill is the stimulus, and the performance is the perception, normal distributed around the hidden value.

Probability Theory provides us with a consistent mathematical framework  for quantifying the uncertainty of our beliefs, and to update them optimally given a model and the data~\cite{bishop2006-patternRecognitionMachineLearning}.

\cite{herbrich2006-trueskill}

\cite{dangauthier2008-trueskillThroughTime}

\cite{coulom2008-wholeHistoryRating}

\cite{maystre2019-pairwise}

@@

\subsection{Solucion exacta}

%\section{Prior predictive y evidencia}

La evidencia es otro nombre para el Prior predictive.
%
\begin{equation*}
\underbrace{P(\text{Belief}|\text{Data})}_{\text{\scriptsize Posterior}} = \frac{\overbrace{P(\text{Data}|\text{Belief})}^{\text{\scriptsize Likelihood}} \overbrace{P(\text{Belief})}^{\text{\scriptsize Prior}} }{\underbrace{P(\text{Data})}_{\hfrac{\hfrac{\text{\scriptsize Evidence or}}{\text{\scriptsize Average likelihood}}}{\text{\scriptsize Prior Predictive}} } }
\end{equation*}

\subsection{Full TrueSkill}

\paragraph{\emph{looseLikelihood}$\bm{(t_{i+1})}$:}

\paragraph{\emph{winLikelihood}$\bm{(t_{i})}$:}
\begin{equation}
 \begin{split}
  \emph{winLikelihood}(t_{i}) = \int \mathbb{I}(d_i>0) \emph{prior}(t_{i+1}) \widehat{\emph{likelihood}}(d_i)
 \end{split}
\end{equation}

\subsection{TrueSkill through Time (TTT)}

\subsubsection{Convergence}

% \begin{table}[t!]
% \centering
% \begin{tabular}{lllp{7.4cm}}
% \hline
% Type           & Distribution & Method   & Description \\ \hline
% GLM            & Poisson      & ML       & Poisson regression: classical GLM,
%                                            estimated by maximum likelihood (ML) \\
% \end{tabular}
% \caption{\label{tab:overview} Overview of various count regression models. The
% table is usually placed at the top of the page (\texttt{[t!]}), centered
% (\texttt{centering}), has a caption below the table, column headers and captions
% are in sentence style, and if possible vertical lines should be avoided.}
% \end{table}
%

\bibliography{article}

\section{Propiedades}\label{sec:propiedades}

@@

\subsection*{Multiplicacion de normales}  
\begin{equation}\label{eq:multiplicacion_normales}
\begin{split}
 \int_{-\infty}^{\infty} N(x|\mu_x,\sigma_x^2)N(x|\mu_y,\sigma_y^2) \, dx  &  \overset{*}{=} \int_{-\infty}^{\infty}  \underbrace{N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2)}_{\text{constante}} N(x|\mu_{*},\sigma_{*}^2) dx \\
 & = N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2) \underbrace{\int_{-\infty}^{\infty}  N(x|\mu_{*},\sigma_{*}^2) dx}_{1} \\
 & = N(\mu_x|\mu_y,\sigma_x^2+\sigma_y^2) 
\end{split}
\end{equation}

@@

\subsection*{Integrales con funci\'on indicadora}
\begin{equation}\label{eq:integral_con_indicadora} 
\begin{split}
 \int_{-\infty}^{\infty}  \int_{-\infty}^{\infty}  \mathbb{I}(x=h(y,z)) f(x) g(y)\, dx\, dy &=  \int_{-\infty}^{\infty} \int_{h(y,z)}^{h(y,z)} f(h(y,z)) g(y)\, dx\, dy\\
 & = \int_{-\infty}^{\infty} f(h(y,z)) g(y) dy 
 %& \propto \int f(h(y,z)) g(y) dy 
\end{split}
\end{equation}

\subsection*{Simetr\'ia de normales}
\begin{equation}\label{eq:simetria}
 N(x|\mu,\sigma^2) = N(\mu|x,\sigma^2) = N(-\mu|-x,\sigma^2) = N(-x|-\mu,\sigma^2) 
\end{equation}

\subsection*{Derivada de la acumulada normal}
\begin{equation}\label{eq:phi_norm}
 \frac{\partial}{\partial x} \Phi(x|\mu,\sigma^2) = N(x|\mu,\sigma^2)
\end{equation}

\subsection*{Distribuci\'on normal estandarizada}
\begin{equation}\label{eq:estandarizar}
 X \sim N(\mu,\sigma^2) \Rightarrow \frac{X-\mu}{\sigma} \sim N(0,1)
\end{equation}

\section{Ejemplo 2 vs 2}

@@

\subsection{Mensajes descendentes}

@@

@@

 \subsection{Aproximacion de la posterior (DRAFT)}

La probabilidad de una diferencia cuando se conoce el resultado (Eq.~\ref{eq:p_d}) es una Normal truncada.
%
\begin{equation}\label{eq:p_d}
\begin{split}
 P(d_1) & \overset{\hfrac{\text{eq}}{\ref{eq:marginal}}}{=}   \prod_{h \in n(d_1)} m_{h \rightarrow d_1} \overset{\hfrac{\text{fig}}{\ref{modelo_trueskill_2vs2}}}{=} m_{f_{d_1} \rightarrow d_1}(d_1) \, m_{f_r \rightarrow d_1}(d_1) \overset{\hfrac{\text{eq}}{\ref{eq:m_fr_d}}}{\underset{\hfrac{\text{eq}}{\ref{eq:m_d_fd}}}{=}}  m_{f_{d_1} \rightarrow d_1}(d_1) \, m_{d_1 \rightarrow f_{d_1}}(d_1)  \\
 & = N(d_1|\delta,\vartheta) \mathbb{I}(d_1 > 0)
\end{split}
\end{equation}
%
Para tener una posterior normal lo que se hace es un buscar la normal que m\'as se aproxima a esta normal truncada

@@

\section{Propiedades de las funciones de densidad Normales}
